Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-01 Papers/ms.tex
More editing

In this paper we address the topic of
inferring the matter distribution in the lens galaxy from the lensed,
blurred image. These approaches may be categorized according to the following
criteria:
\begin{enumerate}
\item Whether to use a simply parameterized (e.g. Sérsic), moderately flexible
(e.g. mixture model, \citet{2011MNRAS.412.2521B})
or free-form (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain
Monte Carlo with or without source parameters marginalized out).
\end{enumerate}

Many different approaches have been proposed and applied to
this problem. Recent sophisicated approaches to
this problem include \citet{2014MNRAS.445.2181C},
\citet{2015arXiv150500198T}, and
\citet{2015arXiv150407629B}. {\bf todo: actually comment
on what's in these papers}.

>>>>

Lens modelling has been a topic of much interest over the last two decades.
Most approaches are based on Bayesian inference or maximum likelihood or
variations thereof. These approaches may be categorized according to the
following criteria:
\begin{enumerate}
\item Whether to use a simply parameterized (e.g. a Sérsic profile),
moderately flexible (e.g. a mixture model, \citet{2011MNRAS.412.2521B})
or free-form (e.g. pixellated) model for the surface brightness profile of the source
\item Whether to use a simply parameterized (e.g. Singular Isothermal Ellipsoid)
or flexible model (e.g. pixellated) for the mass profile of the lens
\item How to compute the results (e.g. optimization methods, Markov Chain
Monte Carlo with source parameters marginalized out analytically, or
with the source parameters included).
\end{enumerate}

Recent sophisicated approaches to
this problem include \citet{2014MNRAS.445.2181C},
\citet{2015arXiv150500198T}, and
\citet{2015arXiv150407629B}. {\bf todo: actually comment
on what's in these papers}.
